A Computational Account of Default-Mode Function\\ by Control Theory and Reinforcement Learning

### 2016-10-07 paper/paper.tex
cleanup RL-PC section

\section{Relation to other cognitive models (Danilo)}
\paragraph{Predictive Coding and Bayesian Brain Hypothesis}
The predictive coding and Bayesian brain framework 
is a frequently evoked idea related to the default mode function
\cite{bar2007}.
Cortical responses emerge from a functional network of continuously interacting high and low hierarchical levels.
A dynamic intercourse performs inference on the world by reconciling gaps between sensory input and prior information. 
Feed-forward sensory experience is constantly modulated by
modulatory top-down modulation at various hierarchical processing levels.
It explains the constructive, generative nature of sensory perception
\cite{friston2010free} and
why motor action is intimately related to sensory expectations
\cite{wolpert1995internal}.
and explains
At each stage of processing abstraction level,
an internally generated prediction of the sensory input is
directly compared against actual external input.
A prediction error, i.e. the difference between sensory input
and internal prediction,
occurring at one of the processing levels
incurs plasticity changes of neuronal back-projections (i.e., model parameters)
for gradually improved future prediction of the environment.
Indeed,
back projection outnumber by far the input projection in the brain
\cite{salin1995corticocortical}.
This process permits updates of beliefs about the world
to best fit the incoming sensory examples.
The generative model of how data are generated in the
world would hence be incorporated by
the current neuronal wiring.
Contextual integration is maintained by top-down modulation of sensorimotor
processing by context-specific a-priori information.
formulate perception as a constructive process
based on internal or generative models.

\begin{itemize}
  \item Both accounts are process theories, supported by
  neurobiological evidence, that
  view the brain as a \"statistical organ\"
  that generalizes from the past to new experiences (Friston 2014).
  \item Both have a notion of brain plasticity with increased
  adaption of neuronal wiring when faced by unprecedented environmental
  challenges.
  \item hierarchical aspects from predictive coding in RL lies in the
  nested prediction of probable upcoming actions and rewards
  \item Both model consequences of action. In RL, the horizon of that
  look into the future is manifest in the $\gamma$ parameter, but not
  explicitly modeled in the PC account.
  \item mismatch negativity of PC is immanent in reward prediction error
  by the difference between actually predicted reward of an action given
  a state and the reward predicted by non-linear regression with graded
  discounting of future rewards
  \item Sensory experience is a generative process from both views.
  In predictive coding sensory perception of the external world
  is a generative experience due to modulatory top down experience at
  various hierarchical levels of sensory input processing.
  In RL, the environmental model is incorporated in the Markov decision
  process, \textit{which can be fully recovered based on the last
  state alone}.
  \item Both provide a parsimoneous explanation why
  humans seem to minimize processing of incoming information
  when the environment is predictable and allocate attention when
  novel stimuli are encountered.
  Similarly, the both propose explanations why
  predicting the future is inherently
  linked to information from the past; similarly for independence across
  geographical spaces.
\end{itemize}

>>>>

\section{Relation to other cognitive models (Danilo)}
\paragraph{Predictive Coding and Bayesian Brain Hypothesis}
The predictive coding and Bayesian brain framework 
is a frequently evoked idea related to the default mode function
\cite{bar2007}.
According to this view,
cortical responses emerge from continuous functional interaction between
higher and lower levels of the neural processing hierarchy.
This dynamic intercourse enables inference on the world by reconciling
gaps between fresh sensory input and stored prior information. 
Feed-forward sensory experience is constantly calibrated by
top-down modulation at various hierarchical processing levels.
back projections probably outnumber by far the existing input projection in the brain
\cite{salin1995corticocortical}.
It can explains the constructive, generative nature of sensory perception
\cite{friston2010free} and
why motor action is intimately related to sensory expectations
\cite{wolpert1995internal}.
At each stage of neural processing,
an internally generated prediction of the sensory input is
directly compared against the actual input from the environment.
A prediction error at one of the processing levels,
i.e. the difference between sensory input
and internally predicted sensation,
incurs plasticity changes of neuronal back-projections (i.e., model parameters)
for gradually improved future prediction of the environment.
Contextual integration is maintained by top-down modulation of sensorimotor
processing by context-specific a-priori information.
The generative model of how data arise in the
world hence be incorporated into
the current neuronal wiring.
Indeed,
This process permits updates of the internal model of the environment
to best fit the incoming sensory examples.

\begin{itemize}
  \item Both accounts are process theories backed up by plausible
  neurobiological evidence that
  view the brain as a \"statistical organ\"
  generalizing from the past to new experiences.
  \item Both expose a mechanisms of brain plasticity with increased
  adaption of neuronal wiring when faced by unprecedented environmental
  challenges.
  \item The hierarchical aspects from predictive coding
  is re-expressed in MDP in form of
  nested prediction of probable upcoming actions and rewards.
  \item Both model the consequences of action. In RL, the horizon of that
  look into the future is manifest in the $\gamma$ parameter
  in the Bellman equation, but not
  explicitly modeled in the PC account that
  mostly emphasizes prediction about the
  immediate future.
  \item Mismatch negativity of PC is immanent in reward prediction error
  by the difference between actually predicted reward of an action given
  a state and the reward predicted by non-linear regression with graded
  discounting of future rewards.
  \item Sensory experience is a generative process from both views.
  In predictive coding, sensory perception of the external world
  is a generative experience due to modulatory top down experience at
  various hierarchical levels of sensory input processing.
  In our RL view, the (partially observed)
  environmental model is incorporated in the Markov decision
  process, \textit{which can be fully recovered based on the last
  state alone}.
  \item Both provide a parsimoneous explanation why
  humans seem to minimize processing of incoming information
  when the environment is predictable and allocate attention when
  novel stimuli are encountered.
  Similarly, both propose explanations why
  predicting the future is inherently
  linked to information from the past.
\end{itemize}
